
```{r setup, include=FALSE, echo=F, warning=F, message=F}
knitr::opts_chunk$set(echo = TRUE)

# Read packages ----------------
library(tidyverse)
library(readxl)
library(knitr)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")    <-- install kableEstr
library(kableExtra)

# Source background working R script ----------------
# note this is poor form for reproducibility but otherwise Rmarkdown suffers major bloat
source("conuma_cn_termrun.R", local = knitr::knit_global())

# Define run year for automation below ----------------
RR_year <- 2021
RR_ages <- data.frame(RESOLVED_AGE=c(2:6))
```

---
title: "**Conuma terminal run (RY `r RR_year`)**"
output: html_document
date: 'Last update: `r Sys.Date()`'
---

<br>

<br> 

### **Introduction** ### 
*This can be amended - taken from original Excel file *

The objectives are to: 

1. Estimate **terminal returns** to the area **by age**. The age breakdown is essential for Chinook forecasting and modelling
2. Estimate the **hatchery contribution** to the terminal runs
3. Estimate the potential **egg deposition**. For Chinook, we are defining escapement targets by eggs due to the variable age-at-return and variable contribution of females to spawner totals.
4. Estimate terminal **harvest rates**

<br>

Data sources include:

* Catch data:
    + Sport age data: from 'BIOCNxxx.xlsx' files. Ages pooled over sub-areas and weighted by stat week sample size. 
    + Sport termal mark data: from '2013 - X:\WCVI\THERMAL_MARK_PROJECT\Data\Biodata\Sport\Area_25_2009to2013Chinook_Bio_Recreational_Crest_oto_age.xlsx' files.
* Escapement data:
    + Query escapement and broodstock estimates from New Escapement Index.xls or from Escapement Coordinator's PDF summaries.
    + Query escapement age data from NuSEDs; cross check with WCVI files for additional data not entered into NuSEDs; sample N is usually higher than for otolith-linked biodata; ages are uncorrected for sex stratified sampling; for RunRecon years, these data were used to calculate age, rather than pulling from PADs directly
    + If otolith data are available and linked to biodata, summarize to determine % marked by age; summarize further to determine % marked by age and sex.
    + Correct escapement sample age data for sex-stratified sampling: 
        + Determine sex at age proportions from biodata
        + Use first set sex ratio data from hatchery staff (Conuma) to calculate correction factors
        + Note: do not correct broodstock age ratio as the hatchery uses 3:3 males:females when spawning (more similar to the sex stratified sample)

**For detailed metadata summaries that contribute to the final summaries, see Appendix A.**

<br>

<br>

### **`r RR_year` Summary Tables** ### 

##### <span style="text-decoration:underline"> 1. Nootka Sound Terminal Return (incl non-local WCVI stocks) </span> #####

*updated after all data in*

##### <span style="text-decoration:underline"> 2. Nootka Sound Terminal Return (Local Area 25 stocks only) </span> #####
(escapement for index stocks only)

*updated after all data in*

##### <span style="text-decoration:underline"> 3. Conuma River Terminal Return (hatchery & natural Conuma) </span> #####

*updated after all data in*

##### <span style="text-decoration:underline"> 4. Conuma River Terminal Return (hatchery Conuma) </span> #####

*updated after all data in*

<br>

<br>

### **`r RR_year` Recreational fisheries summary** ### 

Rec fisheries: `r infill.rec.db %>% group_by(RUN_RECON_AREA2) %>% summarize(RUN_RECON_AREA2 = unique(RUN_RECON_AREA2)) %>% pull(RUN_RECON_AREA2)`

Data used:

```{r echo=F, warning=F, message=F}
infill.rec.db %>% 
  group_by(RUN_RECON_AREA2, MONTH) %>%
  summarize(`Catch data from`=unique(catch_data_source), `Age data from`=unique(age_data_source), `Stock comp data from`=unique(comp_data_source)) %>%
  rename(`Rec fishery`=RUN_RECON_AREA2,
         Month=MONTH) %>%
  kbl(align="c") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>%
  collapse_rows(columns=1, valign="middle", target=1)
```

Recreational fishery catch summary:

```{r echo=F, message=F, warning=F}
table_REC_breakdown %>% 
  mutate(total_kept_by_agecomp = round(total_kept_by_agecomp, 0)) %>%
  arrange(RESOLVED_AGE) %>%
  pivot_wider(names_from = RESOLVED_AGE, values_from = total_kept_by_agecomp) %>%
  filter(!is.na(RUN_RECON_AREA2)) %>%
  mutate_at(c(4:8), ~replace(., is.na(.), 0)) %>%
  arrange(RUN_RECON_AREA2, `TERM_CON 2`) %>%
  rename(`Rec fishery`=RUN_RECON_AREA2,
         Origin=`TERM_CON 2`,
         `Total kept` = total_kept) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  add_header_above(c(" "=3, "Age"=5)) %>%
  collapse_rows(columns=c(1,2), valign="middle", target=1)
```

<br>

<br>

### **`r RR_year` Commercial and 5 Nations fisheries summary** ### 

Commercial fisheries: `r table_COMM_breakdown %>% filter(!is.na(type)) %>% group_by(type) %>% summarize(type=unique(type)) %>%  pull(type)`

Commercial data used:

```{r echo=F, message=F, warning=F}
comm.db %>% 
  filter(!is.na(type)) %>%
  group_by(type) %>%
  summarize(`Catch data from`=unique(catch_data_source), `Age data from`=unique(age_data_source), `Stock comp data from`=unique(comp_data_source)) %>%
  rename(`Commercial fishery`=type) %>%
  kbl(align="c") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) 
```  

Commercial fishery catch summary:

```{r echo=F, message=F, warning=F}
table_COMM_breakdown %>%
  mutate(total_kept_by_agecomp = round(total_kept_by_agecomp, 0)) %>%
  arrange(RESOLVED_AGE) %>%
  pivot_wider(names_from = RESOLVED_AGE, values_from = total_kept_by_agecomp) %>%
  filter(!is.na(stock_hatchery_origin)) %>%
  select(type, total_kept, stock_hatchery_origin, `2`:`6`) %>%
  rename(Origin=stock_hatchery_origin,
         Fishery=type,
         `Total kept` = total_kept) %>%
  arrange(Fishery, Origin) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  add_header_above(c(" "=3, "Age"=5)) %>%
  collapse_rows(columns=c(1,2), valign="middle", target=1)
```

<br>

5 Nations ISBM fisheries: `r table_n5_breakdown %>% filter(!is.na(RUN_RECON_AREA2)) %>% group_by(RUN_RECON_AREA2) %>% summarize(RUN_RECON_AREA2=unique(RUN_RECON_AREA2)) %>% pull(RUN_RECON_AREA2)`

5 Nations ISBM data used:

```{r echo=F, message=F, warning=F}
infill.n5.db %>%
  filter(!is.na(type)) %>%
  group_by(RUN_RECON_AREA2) %>%
  summarize(`Catch data from`=unique(catch_data_source), `Age data from`=unique(age_data_source), `Stock comp data from`=unique(comp_data_source)) %>%
  rename(`5 Nations fishery`=RUN_RECON_AREA2) %>%
  kbl(align="c") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"))   
```  

5 Nations fishery catch summary:  *Note Outer Nootka doesn't match Excel file right now due to discrepancy in documented stock comp %*

```{r echo=F, message=F, warning=F}
table_n5_breakdown %>%
  mutate(total_kept_by_agecomp = round(total_kept_by_agecomp,0)) %>%
  arrange(RESOLVED_AGE) %>%
  pivot_wider(names_from = RESOLVED_AGE, values_from = total_kept_by_agecomp) %>%
  filter(!is.na(`TERM_CON 2`)) %>%
  select(RUN_RECON_AREA2, total_kept, `TERM_CON 2`, `2`:`6`) %>%
  rename(Origin=`TERM_CON 2`,
         `5 Nations fishery`=RUN_RECON_AREA2,
         `Total kept` = total_kept) %>%
  arrange(`5 Nations fishery`, Origin) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  add_header_above(c(" "=3, "Age"=5)) %>%
  collapse_rows(columns=c(1,2), valign="middle", target=1)
```
<br>

<br>

### **`r RR_year` FSC fisheries summary** ### 

<br>

<br>

### **`r RR_year` Conuma Hatchery and river escapement summary** ### 

Coming soon! 

<br>

<br>

### **`r RR_year` Escapement and catch to other indicator systems summary** ### 

Coming soon! 

























































<br>

<br>

<br>

<br>

<br>

<br>

<br>

<br>

--------------------
--------------------

### **Appendix A: Metadata summaries** ### 

Below are summary tables contributing to each fishery/region roll up, similar to the tabs produced in the TERMAL_RUN.xlsx files (e.g., "21_metadata").

<br>

#### **Recreational fishery metadata** ####

##### <span style="text-decoration:underline"> Catch data </span> ##### 

* Source: X:\WCVI\CHINOOK\WCVI_TERMINAL_RUN\Annual_data_summaries_for_RunRecons\2021\2021_SPORT_CATCH_DATA-SC Sport Catch Creel Sub-area Disposition.xlsx
* Note:  2021 Sport stock compositions can't be updated until fall 2022 (2020 comps are used)

```{r echo=F}
conuma.rec.catch %>%
  select(RUN_RECON_AREA2, MONTH, YEAR, total_kept) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=1, valign="middle", target=1)
```

<br>

##### <span style="text-decoration:underline"> Age data </span> ##### 

* Source: 2020-21_CHINOOK_BIODATA_from_CREST-WCVI_CN_RunRecon_Query_28Feb2022.xlsx, sheet="JB - TERMCON PVT"

```{r echo=F}
conuma.rec.ages %>%
  select(RUN_RECON_AREA2, MONTH, age_total, RESOLVED_AGE, age_n, age_propn) %>%
  mutate(age_propn = round(age_propn*100, 1)) %>%
  rename(proportion=age_propn) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1,2,3), valign="middle", target=1)
```

<br>

##### <span style="text-decoration:underline"> Stock comp data </span> ##### 

* Source: 2020-21_CHINOOK_BIODATA_from_CREST-WCVI_CN_RunRecon_Query_28Feb2022.xlsx, sheet="WCVI_Chinook_Run_Rec"

```{r echo=F}
conuma.rec.comp %>%
  select(RUN_RECON_AREA2, MONTH, comp_total, `TERM_CON 2`, comp_n, comp_propn) %>%
  mutate(comp_propn = round(comp_propn*100, 1)) %>%
  rename(proportion=comp_propn) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1:3), valign="middle", target=1)
```

<br>

<br>

#### **Commercial fishery metadata** ####

##### <span style="text-decoration:underline"> Catch data </span> ##### 

* Source: 
    + X:\WCVI\CHINOOK\WCVI_TERMINAL_RUN\Annual_data_summaries_for_RunRecons\2021\2021_SPORT_CATCH_DATA-SC Sport Catch Creel Sub-area Disposition.xlsx
    + X:\WCVI\CHINOOK\WCVI_TERMINAL_RUN\TERMCON\CON2021\Five Nations 2021 Catch by PFMA by Month_nearshore.xlsx

* Note:  2021 Sport stock compositions can't be updated until fall 2022 (2020 comps are used)

```{r echo=F}
aD.catch %>%
  select(YEAR, LICENCE_AREA, catch_data_source, statweek, FISHING_DATE, kept) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1:4), valign="middle", target=1)
```

<br>

##### <span style="text-decoration:underline"> Age data </span> ##### 

* Source: 2020-21_CHINOOK_BIODATA_from_CREST-WCVI_CN_RunRecon_Query_28Feb2022.xlsx, sheet="JB - TERMCON PVT"

```{r echo=F}
aD.age %>%
  select(c(YEAR, SAMPLE_TYPE, age_data_source, statweek, COLLECTION_DATE, RESOLVED_AGE, age_n, age_propn)) %>%
  mutate(age_propn = round(age_propn*100, 1)) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1:4), valign="middle", target=1)
```

<br>

##### <span style="text-decoration:underline"> Stock comp data </span> ##### 

* Source: 2020-21_CHINOOK_BIODATA_from_CREST-WCVI_CN_RunRecon_Query_28Feb2022.xlsx, sheet="WCVI_Chinook_Run_Rec"

* Note: Stock composition proportions are given as daily totals by age (e.g., 5 year old Natural Conuma on Aug 12 (n=1) represented 20% of the total number of age-5s sampled on Aug 12). These ages are not used for final ages though.  

```{r echo=F}
aD.comp %>%
  select(c(YEAR, SAMPLE_TYPE, comp_data_source, statweek, COLLECTION_DATE, DAYOFYEAR, stock_hatchery_origin, RESOLVED_AGE, comp_n, comp_propn)) %>%
  mutate(comp_propn = round(comp_propn*100, 1)) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1:5), valign="middle", target=1)
```

<br>

<br>

##### **5 Nations ISBM Muchalat (Matchlee Bay) and Outer Nootka** #####

##### <span style="text-decoration:underline"> Muchalat (Matchlee) and Outer Nootka catch </span> #####

* Source: X:\WCVI\CHINOOK\WCVI_TERMINAL_RUN\TERMCON\CON2021\Five Nations 2021 Catch by PFMA by Month_nearshore.xlsx

```{r echo=F}
n5.catch %>%
  select(c(year, area, type, RUN_RECON_AREA2, catch_data_source, month, kept_catch)) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1:5), valign="middle", target=1)
```

##### <span style="text-decoration:underline"> Muchalat (Matchlee) and Nootka age </span> #####

* No age data directly sampled in 2021. See main text for data substitutions made.

##### <span style="text-decoration:underline"> Muchalat (Matchlee) and Nootka stock composition </span> #####

* Source: X:\WCVI\CHINOOK\WCVI_TERMINAL_RUN\TERMCON\CON2021\PID20200133_Taaq_A25(20)_sc276_2021-03-23.xlsx

* No stock composition data directly from 5N Outer Nootka ISBM. See main text for data substitutions made. 
* Note: For 5N Muchalat, stock composition data is calculated as a proportion of the total number of samples by age (e.g., 6 year old Conuma fish (n=1) represented 50% of the total number of age-6s encountered). These ages are not used for final ages though.  

```{r echo=F}
n5.comp %>%
  select(c(comp_sample_year, type, comp_data_source, RUN_RECON_AREA2, `TERM_CON 2`, comp_n, comp_total, comp_propn)) %>%
  mutate(comp_propn = round(comp_propn*100, 1)) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1:5), valign="middle", target=1)
```

<br>

<br>

##### **SEP Broodstock age data** #####

##### <span style="text-decoration:underline"> Conuma Hatchery </span> #####

* Source: X:\SC_BioData_Management\6-Scale\Age_Results\2021\All_PADS_2021_CN_Ages_to_22Feb2022.xlsx

```{r echo=F}
sep.ages %>%
  select(Project, age_data_source, Esc_location, age_total, `GR Age2`, age_n, age_propn) %>%
  rename(facility=Project,
         system=Esc_location,
         Age=`GR Age2`) %>%
  kbl(align="c") %>%
  kable_paper("hover", full_width=F, position = "center") %>%
  collapse_rows(columns=c(1:4), valign="middle", target=1)
```





































```{r echo=F, eval=F}
# Backup table printing in case kableExtra becomes unstable 
knitr::kable(table_REC_breakdown %>% 
        mutate(kept_by_agecomp = round(kept_by_agecomp,0)) %>%
        pivot_wider(names_from = RESOLVED_AGE, values_from = kept_by_agecomp) %>%
        rename(`Rec fishery`=rec_fishery,
               Origin=`TERM_CON 2`,
               `Total kept` = total_kept,
               `Fishery data source type` = type),
        format="html", align=rep("c", 8))
```

